---
title: "MSD Homework 3, Problem 2"
author: "Your Name (your uni)"
date: '`r Sys.time()`'
output:
  pdf_document:
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
library(here)
library(scales)
library(modelr)
library(tidyverse)

theme_set(theme_bw())

knitr::opts_chunk$set(echo = TRUE)
```

# Part A

Read in the data

```{r read-data}
data <- read_tsv('polyfit.tsv')
```

# Part B

Shuffle the data and assign each row to one of 5 different folds

```{r shuffle-data}
# make sure to use this seed
set.seed(42)

```

Implement 5-fold cross-validation to compute the average train / test error (RMSE) for each polynomial degree

```{r cross-validate}

```

Make a plot showing the how the train and test error vary with the polynomial degree

```{r plot-cv-curve}

```

# Part C

Select the degree with the lowest average test error and fit a final model for this degree on all of the data

```{r fit-best-model}

```

Make a scatter plot of all of the data with the best-fit model overlayed as a line
```{r plot-best-model}

```

Report the coefficients for the best-fit model

```{r print-best-model-coefficients}

```