---
title: "MSD Homework 4, Problem 2"
author: "Your Name (your uni)"
date: '`r Sys.time()`'
output:
  pdf_document:
    toc: yes
    toc_depth: 3
---

```{r setup, include=FALSE}
library(here)
library(scales)
library(igraph)
library(tidyverse)

theme_set(theme_bw())

knitr::opts_chunk$set(echo = TRUE)

```

# Part A

read in the edge list for 2010 from the `undweighted10.dat` file.

```{r read-edge-list}

```

# Part B

Make a plot of the distribution of edge weights for the entire network. Use a log-log scale and comment on the result. What does it tell you about the distribution of tie strength?

```{r plot-edge-weights}

```

## Your comments

# Part C

Next define a sequence of 12 thresholds on these edge weights from 0 up through 1024 in powers of 2 (i.e., 0, 1, 2, 4, ..., 1024). For each value in this sequence, remove all edges whose weight is below the threshold and construct a network from the remaining nodes and edges.

For each such network, compute:

* The number of nodes in the network
* The number of edges in the network
* The number of connected components in the network
* The fraction of nodes contained in the largest connected component of the network
* The average distance between all pairs of nodes in the network

A for loop over the threshold values is probably easiest here.

```{r compute-stats-by-threshold}

```

# Part D

Plot each of these five quantities (on the vertical axis) as a function of the thresholds used (on a logarithmic horizontal axis), and comment on the shape of them.

What's happening to the number of nodes, edges, and components?
How and why is the average distance between nodes changing?

```{r plot-stats}

```

## Your comments

# Part E

You should notice a peak in the number of connected components as a function of the threshold.
What's happening here?
Explain and provide a visualization of the network at this peak, as well as at the next threshold value beyond the peak.

## Your written answer


```{r plot-network-at-peak}

```